### 2021-01-29 papers/jin-thesis/Chapters/2Theory.tex
Edited thesis

\begin{figure}[H]
	\centering
	\includegraphics[width=0.9\columnwidth]{Figures/OB_vs_BB.PNG}
	\caption[One Bound vs. Both Bound]{\textbf{One Bound vs. Both Bound} \textit{Figure on left}: Prestroke one bound state with labeling scheme 'b-’ and ‘u-’ for bound leg and unbound leg. \textit{Figure on the right}: Poststroke both bound state with labeling scheme ‘n-’ and ‘f-’ for ``near" leg and ``far'' leg. \cite{Capek2017}.}
	\label{fig:OBvsBB}
\end{figure}

@@

With the assumption of thermodyamic equilibrium during the both bound state, we can define the probability of dynein being in that configuration from a Boltzmann distribution and calculate the relative probability of unbinding for that specifc configuration by using a proportionality expression. That is, 
\begin{equation}
	P_{ub}\propto e^{-\beta E_{total}}.
\end{equation}
With this Boltzmann factor, we can also generate a partition function, 
\begin{equation} \label{eqn:partition}
	Z=\sum_{i}e^{-\beta E_{total,i}},
\end{equation}
where $i$ refers to the specific both bound configuration. In order to guarantee an accurate thermodynamic ensemble of both bound configurations, the simulation must run a large number of trials to ensure that the sample space is covered well. The thermodynamic ensemble can then generate an ensemble of steps that can eventually produce smooth statictics. With the partition function defined in Equation (\ref{eqn:partition}), we can also define ensemble averages for both bound statistics, such as the average unbinding rates, unbinding probability, and both bound time. The equations to do so are all shown below in that order:
\begin{equation}
	\langle\rho_{ub, n}\rangle=\frac{\sum_{i}\rho_{ub, n} e^{-\beta E_{total,i}}}{Z}, \indent \langle\rho_{ub, f}\rangle=\frac{\sum_{i}\rho_{ub, f} e^{-\beta E_{total,i}}}{Z}
\end{equation}
\begin{equation}
	\langle P_{ub, n}(L)\rangle = \frac{\langle\rho_{ub, n}\rangle}{\langle\rho_{ub, n}\rangle + \langle\rho_{ub, f}\rangle}
\end{equation}
\begin{equation}
	\langle t_{bb} \rangle =\frac{1}{\langle\rho_{ub, n}\rangle + \langle\rho_{ub, f}\rangle}.
\end{equation}

>>>>

\begin{figure}[H]
	\centering
	\includegraphics[width=0.9\columnwidth]{Figures/OB_vs_BB.PNG}
	\caption[One Bound vs. Both Bound]{\textbf{One Bound vs. Both Bound} \textit{Left}: Prestroke one bound state with labeling scheme 'b-’ and ‘u-’ for bound leg and unbound leg. \textit{Right}: Poststroke both bound state with labeling scheme ‘n-’ and ‘f-’ for ``near" leg and ``far'' leg. \cite{Capek2017}.}
	\label{fig:OBvsBB}
\end{figure}

@@

With the assumption of thermodyamic equilibrium during the both bound state, we can define the probability of dynein being in that configuration from a Boltzmann distribution and calculate the relative probability of unbinding for that specifc configuration by using a proportionality expression. That is, 
\begin{equation}
	P_{ub}\propto e^{-\beta E_{total}}.
\end{equation}
With this Boltzmann factor, we can also generate a partition function, 
\begin{equation} \label{eqn:partition}
	Z=\sum_{i}e^{-\beta E_{total,i}},
\end{equation}
where $i$ refers to the specific both bound configuration. In order to guarantee an accurate thermodynamic ensemble of both bound configurations, the simulation must run a large number of trials to ensure that the sample space is covered well. The thermodynamic ensemble can then generate an ensemble of steps that can eventually produce smooth statictics. With the partition function defined in Equation (\ref{eqn:partition}), we can also define ensemble averages for both bound statistics, such as the average unbinding rates, unbinding probability, and both bound time. The equations to do so are all shown below in that order:
\begin{equation}
	\langle\rho_{ub, trail.}\rangle=\frac{\sum_{i}\rho_{ub, trail.} e^{-\beta E_{total,i}}}{Z}, \indent \langle\rho_{ub, lead.}\rangle=\frac{\sum_{i}\rho_{ub, lead.} e^{-\beta E_{total,i}}}{Z}
\end{equation}
\begin{equation} \label{eqn:ProbTrail}
	\langle P_{ub, trail.}(L)\rangle = \frac{\langle\rho_{ub, trail.}\rangle}{\langle\rho_{ub, trail.}\rangle + \langle\rho_{ub, lead.}\rangle}
\end{equation}
\begin{equation}
	\langle t_{bb} \rangle =\frac{1}{\langle\rho_{ub, trail.}\rangle + \langle\rho_{ub, lead.}\rangle},
\end{equation}
where $trail.$ and $lead.$ signifies a trailing or leading step.

### 2021-01-29 papers/jin-thesis/Chapters/3Methods.tex
Edited thesis

\section{Simulation}
%\textit{Picking Random angles to create random distribution of dynein configurations. Make sure to clarify that the simulation is split into two parts, the monte carlo both bound and brownian one bound. It is done this way in order for MC to generate ensemble of data rather quickly.}\\
%\textit{Include a flow chart.}
Since we want to generate an ensemble of steps, we use the Monte Carlo method to simulate a single step at a time, as opposed to a walk. This allows us to simplify the code into two respective parts (the Monte Carlo both bound and the Brownian dynamics one bound) that cycles repeatedly after the model takes a step. The simulation starts in the both bound state, where the Monte Carlo randomly picks a both bound configuration and calculate the total energy. If the configuration successfully unbinds, then we use the positions of the domains as initial conditions for the one bound simulation and execute the Brownian dynamics. Once the one bound dynein diffuses onto the microtubule and rebinds, the simulation repeats the cycle and generates a completely different both bound configuration for another step. However, the big caveat with this method is that we must initialize the distance between the binding domains, $L$, in order to ensure that our ensemble covers the whole sample space of possible both bound configurations. This will force the measured probabilities to be a function of $L$ and will be addressed later in Section (\ref{sec:DataAna}). The algorithm for the both bound process is shown below:

@@

	\item Calculate the relative unbinding probability from a Boltzmann distribution and add a term to the partition function:
	\begin{equation}
		P_{ub} \propto \rho_{ub}e^{-\beta E_{total, n}}\kappa,
	\end{equation}
	\begin{equation}
		Z=\sum_{n}e^{\beta E_{total, n}}.
	\end{equation}
	We defined a $\kappa$ to normalize the relative unbinding probability and keep it less than 1.

@@

	\item Collect statistics about final displacement and one bound time. Repeat algorithm from step 2.

@@

\section{Constants}
\textit{How we defined our constants based on experiment and pictures.  Need to include figures here of experiment dynein and how we measure the pre and post stroke equilibrium angles.}

\begin{figure}[hbt!]
	\centering
	\includegraphics[width=0.3\columnwidth]{../../plots/burgess-model-figure.pdf}
	\includegraphics[width=0.5\columnwidth]{../../plots/grotjahn-model-figure.pdf}%
	\caption[Experimental Pictures of Dynein for Model Parameters]{\textbf{Experimental Pictures of Dynein for Model Parameters} Left: the both bound model is superimposed over dynein micrograph. The arrow indicates 15nm. Image taken from \cite{burgess2003dynein}.  Right: cryo-electron tomograph of dynein with the one-bound model overlaid. Image taken from \cite{grotjahn}.} 
	\label{fig:ModelParams}
\end{figure}

\section{Parameter Fitting}
\textit{How we will fit our parameters to agree with Yildiz' experimental data of dynein stepping.}

\subsection{Rate Constants}
\textit{Fitting our rate constants were a huge part of our model and how we made sure our dynein can match experimentalist results.}

@@

\section{Data Analysis} \label{sec:DataAna}
\begin{equation}
	p(x_i,x_f)=p(x_f|x_i)p(x_i)
\end{equation}
Bayes' Theorem
\begin{equation}
	p(x_i|L_i)=\frac{p(L_i|x_i)p(x_i)}{p(L_i)}
\end{equation}
\[
	p(x_i|L_i)=\frac{p(x_i)}{p(L_i)} 
\]\[
	p(x_i)=p(x_i|L_i)p(L_i)
\]
Detailed Balance Equation:
\begin{equation}
	p^n(L_i)=T^n(L_f|L_i)p^0(L_i)
\end{equation}
\begin{align}
	T(L_f|L_i)&=I(L_f|x_i)p(x_f|x_i)p(x_i|L_i)\\
	&=p(L_f|x_i)p(x_i|L_i)\\
	&=p(L_f|L_i)
\end{align}

>>>>

\section{Simulation}
%\textit{Picking Random angles to create random distribution of dynein configurations. Make sure to clarify that the simulation is split into two parts, the monte carlo both bound and brownian one bound. It is done this way in order for MC to generate ensemble of data rather quickly.}\\
%\textit{Include a flow chart.}
Since we want to generate an ensemble of steps, we use the Monte Carlo method to simulate a single step at a time, as opposed to a walk. This allows us to simplify the code into two respective parts (the Monte Carlo both bound and the Brownian dynamics one bound) that cycles repeatedly after the model takes a step. The simulation starts in the both bound state, where the Monte Carlo randomly picks a both bound configuration and calculates the total energy. If the configuration successfully unbinds, then we use the positions of the domains as initial conditions for the one bound simulation and execute the Brownian dynamics. Once the one bound dynein diffuses onto the microtubule and rebinds, the simulation repeats the cycle and generates a completely different both bound configuration for another step. However, this method comes with a caveat: we must initialize the distance between the binding domains, $L$, in order to ensure that our ensemble covers the whole sample space of possible both bound configurations. This will force the measured probabilities to be a function of $L$ and will be addressed later in the Data Analysis section (Section \ref{sec:DataAna}). The algorithm for the both bound process is shown below:

@@

	\item Calculate the relative unbinding probability from a Boltzmann distribution and add a term to the partition function:
	\begin{equation}
		P_{ub} \propto \rho_{ub}e^{-\beta E_{total, n}}\kappa,
	\end{equation}
	\begin{equation}
		Z=\sum_{i}e^{\beta E_{total, i}}.
	\end{equation}
	We defined $\kappa$ to normalize the relative unbinding probability to keep it less than 1.

@@

	\item Collect statistics about the final position and one bound time. Repeat algorithm from step 2.

@@

\section{Model Parameters}
%\textit{How we defined our constants based on experiment and pictures.  Need to include figures here of experiment dynein and how we measure the pre and post stroke equilibrium angles.}

We match model paramters concerning dynein's geometry based on experiment by analyzing electron microscopy pictures of dynein. These pictures are shown in Figure (\ref{fig:ParamsPics}), where experimental dynein is in the conformations analogous to the both bound and one bound states. The parameters we can measure from these figures are the domain radii, equilibrium angles, and the stalk and tail lengths.

\begin{figure}[hbt!]
	\centering
	\includegraphics[width=0.3\columnwidth]{../../plots/burgess-model-figure.pdf}
	\includegraphics[width=0.5\columnwidth]{../../plots/grotjahn-model-figure.pdf}%
	\caption[Experimental Pictures of Dynein for Model Parameters]{\textbf{Experimental Pictures of Dynein for Model Parameters} \textit{Left:} Micrograph of both bound dynein with model domains to identify post-stroke equilbrium angles \cite{burgess2003dynein}.  \textit{Right:} Cryo-electron tomograph of one bound dynein for pre-stroke equilbrium angles \cite{grotjahn}.} 
	\label{fig:ParamsPics}
\end{figure}

However, these pictures do not help identify the binding rates ($k_b$, $k_{ub}$) and spring constants ($c_b$, $c_m$, $c_t$), thus making these parameters \textit{free variables} in the model. Fortunately, the Monte Carlo simulation can quickly optimize these free variables and fit different combinations of parameters to  different sets of experimental data. Since we want to replicate Yildiz's observations from Figure (\ref{fig:YildizCorrelation}), the free variables will be optimized according to the slope and y-intercept of the correlation.

\subsection{Rate Constants}
\textit{Fitting our rate constants were a huge part of our model and how we made sure our dynein can match experimentalist results. Maybe bring up sticky rate???}

@@

\section{Data Analysis} \label{sec:DataAna}
As mentioned earlier, the simulation can only collect statistics for a given initial binding domain distance, $L$. This limits the probability data of landing at a final position to be a function of $L$. However, the unsigned distance is insignificant when calculating the step length of either a trailing or leading step. This promotes the new naming scheme of using initial displacement, $x_i$, and final displacement $x_f$, when identifying the distance between the binding domains before and after the step. The displacement is the $x$ position of the unbounded binding domain during the step, where the origin is defined at the bounded binding domain. This implies a negative initial displacement for a trailing step and a positive initial displacement for a leading step.

However, we still suffer with the simulation outputting a probability distribution of final displacements as a function of initial displacements. To properly reproduce Yildiz's stepping plot, we need a joint probability distribution with both $x_i$ and $x_f$ as variables. Using probability notation, we want $p(x_i,x_f)$ (the probability of $x_i$ \textit{and} $x_f$) but we have $p(x_f|x_i)$ (the probability of $x_f$ \textit{given} $x_i$). To solve this problem, we can use conditional probability and solve for $p(x_i,x_f)$, as shown below:

\[
	p(x_f|x_i)=\frac{p(x_i,x_f)}{p(x_i)},
\]
\begin{equation}
	p(x_i,x_f)=p(x_f|x_i)p(x_i).
\end{equation}
Now, we only need to find the probability density of initial displacements, $p(x_i)$. Since the initial displacement is simply a signed distance $L$, we can use the probability of unbinding for a trailing or leading step as a function of $L$ from Equation (\ref{eqn:ProbTrail}) to generate $p(x_i)$. In otherwords, Equation (\ref{eqn:ProbTrail}) gives us $p(x_i|L_i)$. We can relate the two by using Bayes' Theorem:

\begin{equation}
	p(x_i|L_i)=\frac{p(L_i|x_i)p(x_i)}{p(L_i)}.
\end{equation}
Since the probability of an initial distance given the initial displacement, $p(L_i|x_i)$, is always 1, we can simplify further,
\[
	p(x_i|L_i)=\frac{p(x_i)}{p(L_i)} 
\]

\begin{equation}
	p(x_i)=p(x_i|L_i)p(L_i).
\end{equation}
Now, the final step is to solve for the probability density of initial distance, $p(L_i)$. We can do so by solving a Detailed Balance Equation, where we define a transition matrix, $T=p(L_f|L_i)$. This equation will have the form,
\begin{equation}
	p(L_i)=T^np^0(L_i),
\end{equation}
where $T$ is raised to the $n$ number of steps to signify equilibrium for the probability of all distances $L$. $n$ is chosen to be arbitrarily large to ensure equilibrium after enough steps (??? FIXME this reasoning needs to be clearer. Ask Roundy.) To solve for $T$, we can use the previous probability distributions $p(x_f|x_i)$ and $p(x_i|L_i)$ to convert the probabilities to distances, as shown below:
\begin{align}
	T&=I(L_f|x_i)p(x_f|x_i)p(x_i|L_i)\\
	&=p(L_f|x_i)p(x_i|L_i)\\
	&=p(L_f|L_i),
\end{align}
where $I(L_f|x_i)$ is the identity matrix for converting $x_f$ into $L_f$. We have now solved for all the unknowns to generate a joint probability distribution of initial and final displacements, $p(x_i,x_f)$.
